\Large \bf Byteboy : A Byteman Companion application

### 2017-12-08 final-paper/paper.la_.tex
feat(paper): added synthesis section

Majority of the work required for Byteboy is analysing the results from HPROF and presenting it back to the reader in a useful manner. We decided to use Python to handle this task as it was the most accessable and lightweight language available.

@@

This is where we discuss how the rules get mashed together.

@@

Byteman is a powerful tool for tracing and debugging Java programs by injecting code into running application methods, but currently lacks the luxuries of modern programming languages. This paper has presented Byteboy, a companion application suite for Byteman that includes a manual and semi-automatic rule generator, a fuzz test generator, and a VS Code language extension. Byteboy has shown that it can produce rules that may be of use to developers, but will require additional work towards refining and strengthening it's functionality.

@@

\bibitem{yoman}
Yeoman.
\\\texttt{http://yeoman.io/}

@@

@@

\bibitem{byteboy}
Byteboy.
\\\texttt{https://github.com/aptmac/byteboy}

>>>>

Majority of the work required for Byteboy is analyzing the results from HPROF and presenting it back to the reader in a useful manner. We decided to use Python to handle this task as it was the most accessable and lightweight language available.

@@

Byteboy currently offers four different types of rule construction: manual, semi-automatic, automatic, and fuzz test generator.

In manual, Byteboy goes through the required components of Byteman rule syntax, and prompts the user for input for each of the required fields. The end result is a rule constructed based solely on the information provided by the user, and is reminiscent of the Yo Code generator\cite{yocode}.

In semi-automatic, the process is the same as manual, with the addition of information gathered from the analysis phase. Each Byteman rule component (with the exception of the DO block) can be auto-filled by simply pressing the enter key, and Byteboy will supply the highest ranking choice based on the analysis. However, the user is able to freely enter information here as they please, and use the displayed analytics to craft their own rules based on the result of their program's execution.

In automatic, Byteboy creates a set of rules to trace application behaviour. A set of rules are created that alert the console when methods are called, which will provide real-time status reports to the user when running their program with these injected rules.

In fuzz test generator, Byteboy creates a set of rules that are intended to test the durability and resilience of the source program. Byteboy uses the analysis data, and figures out what the data type of each functions parameters are. Next, a rule is constructed that replaces the variable in the function declaration with a randomized value provided by one of our many helper functions. We currently have functionality to randomize the information of int, long, float, double, boolean, and String data types. The goal of these generated rules are to see if randomized inputs can be used to crash the source program, or cause ill effects.

@@

Byteman is a powerful tool for tracing and debugging Java programs by injecting code into running application methods, but currently lacks the luxuries of modern programming languages. This paper has presented Byteboy, a companion application suite for Byteman that includes a manual and semi-automatic rule generator, a fuzz test generator, and a VS Code language extension. Byteboy has shown that it can produce rules that may be of use to developers (for tracing and fuzzing purposes), but will require additional work towards broadening and strengthening it's functionality.

@@

\bibitem{yoman}
Yeoman: The web's scaffolding tool for modern webapps.
\\\texttt{http://yeoman.io/}

@@

\bibitem{byteboy}
Byteboy: A Byteman Companion Application.
\\\texttt{https://github.com/aptmac/byteboy}

@@
